---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# groverr

<!-- badges: start -->
<!-- badges: end -->

The goal of groverr is to make it easy to import data from ESO sources, CAD, and manipulate it.

## Data Sources

### ESO Data
Groverr expects ESO data to be downloaded from Ad Hoc to a single directory with the following specifications:

  - Flat file CSV
  - Name: Either "YYYY-MM{table_name}" or "YYYY_{table_name}" with the table names following a pattern that isn't necessarily logical.
  - 


## Getting Started

Importing ESO data:
```{r example, eval=FALSE}
library(groverr)
## set file_root
file_root <- get_file_root()

## set year and month
year <- set_year()
month <- set_month()

## import incidents (general function)
incidents <- import_eso_data(year, month, "incidents")

## import incidents (specific function)
incidents <- import_incidents(year, month)
```

Note that you have to set file_root first, as the path to the ESO data may vary based on machine, OS, or network. Years and months are passed as strings, and serve as the filter to get into the right flat file. I know, it's clunky.

Custom import functions ensure consistent typing, and more:

  - import_patients
  - import_incidents: adds `dtDate` for incident and `month`, which is YYYY-MM format
  - import_vitals: adds `vsDate` as date time field
  - import_treatments: Combines General, Airway, Cardiac, Medications, and IV treatments (but strangely not labs). Also adds treatmentDate datetime field.
  - import_stroke: Handles some unknown stuff.
  - import_narrative
  - import_cpr: handles some things. TODO here.
  - import_all_data (imports all years/months/etc.) __Garbage function__
  - filtered_incidents: Uses an existing data set to filter incidents for import. TODO here with example.
  
## ESO Data Transformations
- join_crew: Adds Lead, Driver fields.
- cardiac_arrest: Adds OHCA field. __Deprecate in favor of is_cardiac_arrest__.
- rsi: Adds field for RSI meds or not
- rsi_onscene
- blood

## Importing CAD
- get_cad_incidents(server, database, UID, PWD, agency, tzone="US/Central")
  

## Notes
FILE ROOTS:
```{r file_roots}
#file_root <- "C:/Users/skordik/OneDrive - Cypress Creek Emergency Medical Services/March Data/"
#file_root <- "/Users/samuelkordik/OneDrive - Cypress Creek Emergency Medical Services/March Data/"
#file_root <- "W:/Monthly ESO Data/"
```

DB Connection (old):
```{r db_connection}
  # con <- dbConnect(odbc(),
  #                  Driver = "SQL Server",
  #                  Server = "cadsql",
  #                  Database = "CypressCreekCAD",
  #                  UID = "CadSQLUser",
  #                  PWD = "CadSQLUser")
```


